Data Management for LSST Special Programs

### 2023-10-17 sec_intro.tex
fix typos

This is a Rubin Data Management term used used to describe processing that 
uses components of the LSST Science Pipelines and is applied by Rubin
Data Management to images from Special Programs.
Special Processing creates data products that are unique and separate from those produced
by regular processing for the WFD program.

@@

For a list of the mini-surveys under consideration,
see \citeds{PSTN-055}).

>>>>

This is a Rubin Data Management term to describe processing that 
uses components of the LSST Science Pipelines and is applied by Rubin
Data Management to images from Special Programs.
Special Processing creates data products that are unique and separate from those produced
by regular processing for the WFD program.

@@

For a list of the mini-surveys under consideration,
see \citeds{PSTN-055}.
